%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Raul}{Pegan}{% \urlstyle{same}%%\url{http://example.com} \\
\href{mailto:raulpegan1@gmail.com}{raulpegan1@gmail.com} | 619.788.4672
}

%\href{http://linkedin.com/in/12346}{http://linkedin.com/in/12346}

\section{Experience}

\runsubsection{Talke Lab}
\descript{| Esophageal Deflection Device }
\location{June 2017 – Present | University of California, San Diego}
\begin{tightemize}
\item Developed an embedded system for a medical device that deflects the esophagus away from the heart during cardiac ablation surgeries performed on atrial fibrillation patients. Publication pending submission.
\item Designed the analog circuit, MCU firmware, data processing, and automation. 
\end{tightemize}
\sectionsep

\runsubsection{The Art of Product Engineering}
\descript{| Staff Research Associate \& Teaching Assistant }
\location{June 2016 – Present | University of California, San Diego}
\begin{tightemize}
\item Led the creation of a new upper division course for the Electrical \& Computer Engineering department focusing on the creation of a full stack IoT application development. 
\item Developed the IoT ecosystem, from hardware stack composed of embedded Linux ARM devices attached to a custom REST API and web framework.
\end{tightemize}
\sectionsep

\runsubsection{Broadcom}
\descript{| Bluetooth SVT, Intern}
\location{Jun 2015 – September 2015 | Rancho Bernardo, CA}
\begin{tightemize}
\item Developed testing frameworks for the software and firmware of the Broadcom Bluetooth stack.
\item Created a new automated regression testing environment using Perl and C to replace older systems. 
\end{tightemize}
\sectionsep

\runsubsection{activCirk}
\descript{| Software Design Engineer, Intern}
\location{February 2015 – June 2015 | San Diego, CA}
\begin{tightemize}
\item  Created a tool that geometrically analyzes the floorplan of MMIC GDS files and checks for design rule violations.
\item Customized the DRC tool for the unique analog circuit process the company relies on.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Custom Scheduler for Linux}
\descript{| C, ARM Assembly, Linux Kernel}
\begin{tightemize}
\item Developed custom kernel modules for a Raspberry Pi in order to access PMU readings and write a scheduler.
\item Characterized the different provided workloads in order to best implement the LIST scheduler.
\end{tightemize}
\sectionsep

\runsubsection{Branch Prediction Simulation}
\descript{| C}
\begin{tightemize}
\item Simulated a variety of branch predictors from ghsare to tournament. 
\item Created a custom predictor to maximize the efficiency given the provided constraints.
\end{tightemize}
\sectionsep

\runsubsection{Autograder}
\descript{| Django, Python, CSS, HTML}
\begin{tightemize}
\item Created an automated testing framework to grade student assignments using GitHub webhooks.
\item Displayed grading information and notes to students via a custom dashboard.
\end{tightemize}
\sectionsep

\section{Education}
\runsubsection{University of California, San Diego}
\descript{| MS in Computer Engineering}
\location{Expected June 2019 | La Jolla, CA \textbullet{} Cum. GPA: 3.67}
\sectionsep

\runsubsection{University of California, San Diego}
\descript{| BS in Computer Engineering}
\location{June 2016 | La Jolla, CA} 
\sectionsep

\section{Languages}
\begin{minipage}[t]{.6\textwidth}
\subsection{Programming}
C \textbullet{} Python \textbullet{} Perl \textbullet{} Verilog \textbullet{}
SQL \textbullet{} Perl \textbullet{} Javascript\\ \LaTeX\ \textbullet{} C++ \textbullet{} CSS \textbullet{} PHP \textbullet{} Assembly \\
\\Arch Linux + i3 + Vim enthusiast 
\sectionsep
\end{minipage}
\hfill
\begin{minipage}[t]{.35\textwidth}
\subsection{Spoken \& Written}
\location{Native fluency:} English, Spanish\\
\location{Professional working proficiency:} Italian\\
\end{minipage}

\end{document}  \documentclass[]{article}